---
title: "Question 2: London Weather"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Wesley Williams
Ref1: Stellenbosch University
Email1: 21691126\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Is the weather in London as good as Cape Town? No, no it is not.
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(xtable)
library(lubridate)
library(glue)
library(cowplot)

list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

#read in the data
london <- read.csv("data/London/london_weather.csv")
UK <- read.csv("data/London/UKMonthly_Detailed.csv")

#First I need to make sure the date is in the right format using lubridate
weather <- london %>% 
    mutate(date = ymd(date))
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

## Is the weather better in the midlands of England or London?
Let's start with temperature, The graphs below show that not only does London have better weather than the midlands, but the maximum temperature in both places is still colder than Cape town. 

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "London Tempreture\\label{Figure1}", fig.ext = 'png', fig.height = 7, fig.width = 10}


tp <-Temp_plotter(weather, place ="London")


#Lets compare this to the midlands where she wants to move
#First letss limit the sample to just the last 50 years
#names(UK) #get the names in the console fot ease of comparison to the pdf doc
temp <- UK %>% 
    mutate(date = ym(DATE)) %>% 
    select(date, TAVG, TMAX, TMIN) %>% 
    rename("mean_temp" ="TAVG", "min_temp" = "TMIN","max_temp" = "TMAX") #rename so we can use the previous function
tp2 <-Temp_plotter(temp, place ="Midlands")

bothplots <- plot_grid(tp, tp2, ncol = 1)

bothplots


    
```

## Is it more sunny or cloudy?
Now that it has been shown that the weather is better in the London than the midlands let's look at whether London is more sunny than cloudy. The graph below shows that its has only been more sunny than cloudy for 1 year (2014) since 1978. Not only that but the rate of sunshine seems to be decreasing over time as well. So it is pretty much colder, more cloudy and more miserable.

```{r Figure2,  warning =  FALSE, fig.align = 'center', fig.cap = "London is getting less and less sunshine \\label{Figure2}", fig.ext = 'png', fig.height = 7, fig.width = 10}


hs<-hist_sun_plotter(weather)
hs
```

## Rain, rain and rain
We all know that Cape Town has winter rain, but that is okay cause that is when it is cold so you will be inside anyway. In London however it seems to be raining all the time. In Cape Town we can enjoy summer because it barely rains but in London its going to be cold in winter, and then in summer it is just going to rain. I hope you find a lovely house if you do move because you are going to be spending most of your time inside.

```{r results= 'asis'}

rt <- raintable(weather, Latex = FALSE)
rt
```


