---
title: "Question 1: COVID-19"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Wesley Williams
Ref1: Stellenbosch University
Email1: 21691126\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 12pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')



if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(xtable)
library(lubridate)
library(glue)
library(ggplot2)
library(cowplot)
library(rmsfuns)

#Source my code/funcrions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
#First lets load the data in

covid <- read.csv("data/Covid/owid-covid-data.csv")
deaths <- read.csv("data/Covid/Deaths_by_cause.csv")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

## Africa and Covid
Covid-19 was a global catastrophe and it is no secret that different parts of the world were effected differently. The figures below show the total number of cases and total number of deaths by continent. It was common belief at the start of the pandemic that Africa would be effected the most due to the high levels of poverty, lack of health infrastructure compared to the rest of the world and areas with high population density. These figures show that this was a misconception as Africa has the least amount of cases and second least amount of deaths. Mismeasurement is of course a concern but it is highly unlikely that it would change the results substantially as Oceania is the closest with respect to total cases and they has nearly double the amount of total cases. Again when looking at deaths the gap between Asia and Africa is so large that mismeasurement is not a valid excuse. It would be highly informative to attempt to quantify why this was the case. I am of the opinion that Africans have better immune systems due to the standard of living on the continent that it was easier to fight the virus. South America on the other hand was effected the most and as I show later this can be partially attributed to the the lack of change in hospital facilities.
```{r warning =  FALSE, fig.align = 'center', fig.cap = "Evolution of COVID\\label{Figure1}", fig.ext = 'png', fig.height = 8, fig.width = 7}


ep1 <- evolutionplotter(covid)

ep2 <- evolutionplotter2(covid)

bothplots <- plot_grid(ep1, ep2, ncol = 1)

bothplots
```

## Respitory Deaths before and during Covid
Another idea that recieved a lot of attention during the pandemic was the effect of smoking and the severity of Covid. To investigate this I found the 3 countries with the highest rate of smokers (Russia, Greece and Montenegro) all with nearly 90% of their population being smokers and the 3 countries with the lowest rate of smoking (Ghana, Ethiopia and Nigeria) all with less than 10% of their populations being smokers. This could also be a reason as to why Africa was least effected as they have smaller rate of smokers compared to the rest of the world. The table shows that the death rates due to respitory illness (which is what Covid is) increased at a much higher rate for top smoking countries. This shows that smoking definitely did increase the dangers of Covid.

```{r, results = 'asis'}


SmokerTable <- smoker_death_tabular(covid, Latex = FALSE, CountryList = c("Greece", "Russia", "Montenegro", "Ghana", "Ethiopia", "Nigeria"))

SmokerTable

    
```

## Hospitalisation Facilities and ICU admissions

For this section I chose to use just three continents (Europe, Asia and South America). Europe showd that increased hospitilastion facilities led ICU admissions and in the early stages of 2020 actually helped to reduce admissions. In Asia, it lagged as it was constant until late 2021 which did lead the final wave of admissions. Lastly, South America seemed to do nothing to improve hospital facilities and their beds per thousand of people was constant throughout the whole pandemic which definitely contributed to being effected the worst out of all the continents.
```{r warning =  FALSE, fig.align = 'center', fig.cap = "Evolution of Hospitals\\label{Figure2}", fig.ext = 'png', fig.height = 8, fig.width = 7}

h <- ICU_Plotter(covid)

h

```

