---
title: "Question 3: Coldplay vs Metallica"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Wesley Williams
Ref1: Stellenbosch University
Email1: 21691126\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Abstract to be written here. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(xtable)
library(lubridate)
library(ggplot2)
library(glue)
library(cowplot)
library(rmsfuns)

#Source my code/funcrions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

#Read in the data
cold <- read.csv("data/Coldplay_vs_Metallica/Coldplay.csv")
cold <- cold %>% 
    rename("album" = "album_name")
metal <- read.csv("data/Coldplay_vs_Metallica/Metallica.csv")
spotify <- read.csv("data/Coldplay_vs_Metallica/Broader_Spotify_Info.csv")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Popularity by album 

The two figures below show that Coldplay's discography is slightly more volatile than Metallica's in terms of popularity but overall are more popular. 
```{r warning =  FALSE, fig.align = 'center', fig.cap = "Coldplay\\label{Figure1}", fig.ext = 'png', fig.height = 10, fig.width = 10}
#Firstly lets make a function to get the boxplots for both bands


  
coldbp<-box_plotter(cold, Band = "Coldplay")
coldbp
```

```{r warning =  FALSE, fig.align = 'center', fig.cap = "Metallics\\label{Figure2}", fig.ext = 'png', fig.height = 10, fig.width = 10}

metalbp<-box_plotter(metal, Band = "Metallica")
metalbp
```

```{r}
#I think Linkin Park is a fantastic example of a Band that has chnaged what they do and are still popular

# linkin <- spotify %>%
#     filter(artist == "Linkin Park") %>%
#     select(energy,)

#Now lets look at how energy relates to popularity
 #unfortunatly there is no popularity score for LINKIN PARK


```
## Components of each Band: What drives Their Popularity?

Now I show the correlation of identifying factors of both bands with popularity. I start with energy and it seems that firstly Coldplay are much more diverse as they have songs ranging from nearly 0 whereas Metallica's songs are clusered close to 1. Coldplay seem to have an optimal energy level of between 0.4 and 0.6 and Metalica is more popular between 0.75 and 1. 

```{r warning =  FALSE, fig.align = 'center', fig.cap = "Metallics\\label{Figure3}", fig.ext = 'png', fig.height = 7, fig.width = 8}
 #now lets look at the factors that can influence the popularity, Metallica is a metal band so i would expect tempo and energy to be a prominant factor whereas i would expect coldplay to rely on energy and liveness, first i need to combine the data

cold1 <- cold %>% 
    mutate(Band = "Coldplay") %>% 
    select(release_date, name, album, popularity, energy, danceability, tempo, valence, Band) %>% 
            filter(!grepl("Remaster", album),!grepl("Box Set", album), !grepl("Live", album), !grepl("Live", name))


metal1 <- metal %>% 
    mutate(Band = "Mettalica") %>% 
    select(release_date, name, album, popularity, energy, danceability, tempo, valence, Band) %>% 
            filter(!grepl("Remaster", album),!grepl("Box Set", album), !grepl("Live", album), !grepl("Live", name))


battle <- bind_rows(cold1, metal1)
    
#Now i want to look at the popularity vs energy and then get different colours and a line for each


ep <- correl_energy_plotter(battle)
ep

```

Next looking at tempo, again Coldplay is more diverse with their songs ranging from 60 beats per minute to over 200 whereas Metallica only ranges from 75 to just under 200. Metallica's popularity increases with Tempo.

```{r warning =  FALSE, fig.align = 'center', fig.cap = "Metallics\\label{Figure4}", fig.ext = 'png', fig.height = 7, fig.width = 8}

tp <-correl_tempo_plotter(battle)
tp
```
Lastly I looked at Valence. 
Valence is a measure of the degree of positive or negative sentiment associated with a particular experience, object, or event, typically represented on a scale from 0 to 1, where 0 indicates negative valence and 1 indicates positive valence. It reflects the subjective assessment of the emotional tone or quality of the subject matter. Coldplay is more popular with lowe levels so their most popular songs are more sad songs and Metalica's popularity increases with valence so their more upbeat songs are more popular on average.

```{r warning =  FALSE, fig.align = 'center', fig.cap = "Metallics\\label{Figure5}", fig.ext = 'png', fig.height = 7, fig.width = 8}
vp <- correl_valence_plotter(battle)
vp
```


##Most popular song by album and year. Both Metallica and Coldplay's most popular songs seem to have more energy through the years. Coldplay's tempo seems to decrease over time wheras Metallica's tempo has been relatibely constant.
```{r results='asis'}


pop_table <- table_popular(battle, Latex = FALSE)
pop_table
```

