---
title: "Question 4: Netflix"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Wesley Williams
Ref1: Stellenbosch University
Email1: 21691126\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 14pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Lets look at what movies are the best and what makes them good and popular
---
<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(lubridate)
library(glue)
library(xtable)
library(RColorBrewer)


#Source my code/funcrions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

#read in the data
credits <- read.csv("data/netflix/credits.csv")
title <- read.csv("data/netflix/titles.csv")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Best Actors and Directors

```{r}
#Lets try and merge the data to do this I want to get the credits data into a long format with the row for each movie/series
check<-unique(credits$role)
#There are only actors and directors so I need to differentiate between them 
credit <- credits %>% 
  group_by(id) %>% 
  summarise(actors = paste(name[role == "ACTOR"], collapse = ", "),
            directors = paste(name[role == "DIRECTOR"], collapse = ", "),
            .groups = "drop")

#Now i can left join the credits to the title
netflix <- left_join(title, credit, by = "id")
# Now i have a merged data set with the actors and directors and i want to look at which actors and directors are associated with the top movies
```
Below are tables of actors that on average have the best average critic ratings and audience ratings. It would be beneficial to have any movies that has these actors and directors as they are likely to be the most highest rated movies. 
```{r results='asis'}

toptable <-top_table(netflix, Latex = FALSE)
toptable
```

```{r results='asis'}
#Lets also do it for audience scores

aud_top<-audience_top_table(netflix, Latex = FALSE)
aud_top

```

## Genres to Focus on
Below is a plot of the audience and critic rated most popular movies by genre. There is a line at 6.5 to show movie genres that consistently get good ratings. If you want the best rated genres I would suggest getting historical war movies, documentaries and music movies. If you care more about popularity I would suggest animation, sci-fi fantasy, western and action. I think the best movies to have are war movies as they are the best of both worlds.

```{r warning =  FALSE, fig.align = 'center', fig.cap = "Popularity and Ratings by Grenre\\label{Figure1}", fig.ext = 'png', fig.height = 8, fig.width = 10}


gp<-Genre_plotter(netflix)
gp
```
## Words in descriptions

Lastly I show a wordcloud of the most popular words in descriptions of movies that have a audience rating of more than 7. This shows what the best movies use to market themselves and what the most popular themes among audiences. Clearly movies about love, friends and family are the most popular.

```{r  warning =  FALSE, fig.align = 'center', fig.cap = "Frequency of Words in Top Movie Descriptions\\label{Figure2}", fig.ext = 'png', fig.height = 7, fig.width = 10}

wc<-wordcloud_plotter(netflix)
wc

```

